---
title: "Class 9 02052020"
author: "Jenny"
date: "2/5/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## K-means clustering

Let's try the `kmeans()` function

```{r}
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))

plot(x)

```


Use the `kmeans()` function setting k to 2 and nstart to 20
```{r}
km <- kmeans(x, centers = 2, nstart = 20)
```

Inspect the result
```{r}
km

```

What is in the output object
```{r}
attributes(km)
```

Q. How many points are in each cluster?
```{r}
km$size
```

Q. What component of your result object details
    -cluster size
    -cluster assignment/membership
    -cluster center
    
```{r}
km$cluster

table(km$cluster)
```

Plot it out
```{r}
plot(x, col=km$cluster+4)
points(km$centers, col=7, pch=15, cex=2)
```

##Hierarchal clustering
Do not need to know how many clusters to expect from the final analysis
# First we need to calculate point (dis)similarity
# as the Euclidean distance between observations
```{r}
dist_matrix <- dist(x)
```

# The hclust() function returns a hierarchical
# clustering model
```{r}
hc <- hclust(d = dist_matrix)
plot(hc)
abline(h=6, col="red", lty=2)
```

```{r}
cutree(hc, h=6)
```

```{r}
table(cutree(hc, h=3.5))
```

# Using different hierarchical clustering methods

```{r}
# Step 1. Generate some example data for clustering
x <- rbind(
 matrix(rnorm(100, mean=0, sd=0.3), ncol = 2), # c1
 matrix(rnorm(100, mean=1, sd=0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean=1, sd=0.3), # c3
 rnorm(50, mean=0, sd=0.3)), ncol = 2))
colnames(x) <- c("x", "y")

# Step 2. Plot the data without clustering
plot(x)

# Step 3. Generate colors for known clusters
# (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```

Q. Use the dist(), hclust(), plot() and cutree()
 functions to return 2 and 3 clusters
 
```{r}
hc <- hclust(dist(x))

plot(hc)
```
 
#see three major groups, so use cutree to make three clusters
```{r}
grps3 <- cutree(hc, k=3)
table(grps3)
```

 
Q. How does this compare to your known 'col' groups?

```{r}
plot(x, col=grps3+3)
```




## PCA of Eating Habits in the UK
```{r}
x <- read.csv("UK_foods.csv", row.names = 1)
x
```

```{r}
barplot(as.matrix(x), beside=T, col=rainbow(nrow(x)))
```

```{r}
pairs(x, col=rainbow(10), pch=16)

```

```{r}
# Use the prcomp() PCA function 
pca <- prcomp( t(x) )
summary(pca)
```
Looking at the data for proportion of variance, you can see that that PC1 accounts for 67% of the variance and PC2 accounts for 29%, meaning that if you compare PC1 and PC2 you can account for 96.5% of the variance between the data sets


```{r}
# Plot PC1 vs PC2
plot(pca$x[,1], pca$x[,2], xlab="PC1 (67.5%)", ylab="PC2 (29.1%)", xlim=c(-270,500))
text(pca$x[,1], pca$x[,2], colnames(x), col=c("black", "red", "blue", "darkgreen"))
```

