---
title: "Structural Bioinformatics pt. 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB Statistics
Download a CSV file from the PDB site (accessible from “Analyze” > “PDB Statistics” > “by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and use it to answer the following questions:

Q: What percentage of structures in the PDB are solved by X-Ray and Electron Microscopy.

## Read in the file

```{r}
stats <- read.csv("Data Export Summary.csv", row.names = 1)
```

```{r}
ans <- round(stats$Total / sum(stats$Total) *100, 2)
names(ans) <- rownames(stats)
ans
```

Q: What proportion of structures in the PDB are protein?

```{r}
round(sum(stats$Proteins) / sum(stats$Total) *100, 2)
```

Q: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?

```{r}
library(bio3d)

pdb <- read.pdb("1hsg")
pdb
```

```{r}
aa <- get.seq("1ake_A")
aa
```

Adenylate kinase structures from the PDB for analysis

```{r}
hits <- NULL
hits$pdb.id <- c('1AKE_A','4X8M_A','6S36_A','6RZE_A','4X8H_A','3HPR_A','1E4V_A','5EJE_A','1E4Y_A','3X2S_A','6HAP_A','6HAM_A','4K46_A','4NP6_A','3GMT_A','4PZL_A')
```

# Download reLeated PDB files
```{r}
files <- get.pdb(hits$pdb.id, path="pdbs", split=TRUE, gzip=TRUE)
```

## Align reLeated PDBs
```{r}
pdbs <- pdbaln(files, fit = TRUE, exefile="msa")
```
```{r}
# Vector containing PDB codes for figure axis
ids <- basename.pdb(pdbs$id)

# Draw schematic alignment
plot(pdbs, labels=ids)
```

```{r}
library(bio3d.view)
view(pdbs)
```

## PCA on PDBs
```{r}
pc <- pca(pdbs)
plot(pc)
```

```{r}
# Calculate RMSD
rd <- rmsd(pdbs)

# Structure-based clustering
hc.rd <- hclust(dist(rd))
grps.rd <- cutree(hc.rd, k=3)
```

```{r}
plot(pc, 1:2, col="grey50", bg=grps.rd, pch=21, cex=1)
```

```{r}
# Visualize first principal component
pc1 <- mktrj(pc, pc=1, file="pc_1.pdb")
```

