---
title: "Coronavirus"
author: "Jenny"
date: "3/4/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```


> Q1. How many total infected cases are there around the world?

```{r}
total_cases <- sum(virus$cases)
total_cases
```

Lets have a look at the *$type* column

```{r}
table(virus$type)
```

> Q2. How many deaths linked to infected cases have there been?

```{r}
inds <- virus$type =="death"
death_cases <- sum(virus[inds,"cases"])
death_cases
```


> Q3. What is the overall death rate?

Percent death

```{r}
round(death_cases/total_cases * 100, 2)
```


> Q4. What is the death rate in "Mainland China"?

```{r}
allregions <- virus$Country.Region
mainland_china <- allregions == "Mainland China"
sum(mainland_china)

inds <- virus$type =="death"
death_cases <- sum(virus[inds,"cases"])
death_cases
```


> Q5. What is the death rate in Italy, Iran and the US?

```{r}

```

Submit a link to your knited GitHub document (i.e. the md file)
