---
title: "Structure based drug design"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download and process starting structure

Here we download and clean up the structure of HIV-Pr (PDB code: 1HSG) from the main PDB database. We will make a separate set of "protein only" and "ligand only" files.

```{r}
file.name <- get.pdb("1hsg")
HIVpdb <- read.pdb("1hsg")
```

We will use `read.pdb()`, `atom.select()`, and `write.pdb()` functions to make our separate "protein only" and "ligand only" PDB files

## Protein only

```{r}
prot <- atom.select(HIVpdb, "protein", value = TRUE)
write.pdb(prot, file = "1hsg_protein.pdb")
prot
```

## Ligand only

```{r}
lig <- atom.select(HIVpdb, "ligand", value = TRUE)
write.pdb(lig, file = "1hsg_ligand.pdb")
lig
```

## Docking

To visualize the docks and compare to the crystal conformation of the ligand we will create a PDB format file that can be loaded into VMD or PyMol

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
res
```

```{r}
# res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```

